Artus -- Framework for Event-based Data Analysis in High Energy Physics

### 2015-09-07 Core/doc/latex/paper.tex
paper.tex: change to paper.tex document class, removed one level of sections

%\documentclass[a4paper,oneside,BCOR12.5mm,ngerman,12pt]{scrartcl}
\documentclass[a4paper, oneside, 10pt]{scrartcl}

@@

\begin{document}
\section{Development of a General Analysis Framework in C++ \label{section_artus}}

\subsection{Common Workflow of High Energy Physics Analyses \label{section_artus_analysis_workflow}}

@@

\subsection{The Artus Framework \label{section_artus_motivation}}

@@

\subsection{Structure of the Framework \label{section_artus_structure}}

@@

\subsection{Building an End-user Analysis \label{section_artus_analysis}}

@@

\subsection{HarryPlotter -- Python Post-processing Framework \label{section_artus_harryplotter}}

@@

\subsection{A Real World Application -- the $\PH\to\Pgt\Pgt$ Analysis \label{section_artus_example_htt}}

>>>>

% http://www.elsevier.com/authors/author-schemas/latex-instructions
% http://ftp.math.purdue.edu/mirrors/ctan.org/macros/latex/contrib/elsarticle/doc/elsdoc.pdf
\documentclass[3p]{elsarticle}

@@

% http://latex-community.org/forum/viewtopic.php?f=4&t=11123#p42875
\makeatletter
\def\ps@pprintTitle{%
  \let\@oddhead\@empty
  \let\@evenhead\@empty
  \def\@oddfoot{\reset@font\hfil\thepage\hfil}
  \let\@evenfoot\@oddfoot
}
\makeatother

\begin{document}

\begin{frontmatter}
\title{Artus -- Framework for Event-based Data Analysis in High Energy Physics}

\author[kit]{Thomas M\"uller}
\address[kit]{Karlsruhe Institute of Technology, Wolfgang-Gaede-Stra\ss{}e 1, D-76131 Karlsruhe}

\begin{abstract}
abstract
\end{abstract}

%\begin{keyword}
%keyword
%\end{keyword}
\end{frontmatter}

\section{Common Workflow of High Energy Physics Analyses \label{section_artus_analysis_workflow}}

@@

\section{The Artus Framework \label{section_artus_motivation}}

@@

\section{Structure of the Framework \label{section_artus_structure}}

@@

\section{Building an End-user Analysis \label{section_artus_analysis}}

@@

\section{HarryPlotter -- Python Post-processing Framework \label{section_artus_harryplotter}}

@@

\section{A Real World Application -- the $\PH\to\Pgt\Pgt$ Analysis \label{section_artus_example_htt}}
